Unifying Gompertzian growth with the communicable disease spreading paradigm

### 2022-06-09 letterToEditor/letter.tex
fix small things
updates

\recipient{To}{Editor, \\
               Proceedings of the National Academy of Sciences,\\ 
               }
\date{\today}
\opening{\textbf{Initial submission of manuscript titled: ``Unifying Gompertzian growth with the communicable disease spreading paradigm''}}
\closing{Sincerely yours, \vspace{-1em}}

\enclosure[Enclosed ]{
              \\ List of referees, NAS members and PNAS editorial board members
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\        
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
                 }
\makelettertitle

@@

Further, as we wish to have a double-blind review process, our names are omitted in the manuscript.

@@

\textbf{List of Editorial board members}
\begin{enumerate}
\item Levine, Herbert
\item Levin, Simon A.
\item Marquet, Pablo A.
\end{enumerate}

\textbf{List of NAS members (in order of relevance)} 
\begin{enumerate}
\item Levine, Herbert
\item Levin, Simon A.
\item Michael Levitt

\item Nigel D. Goldenfeld 
\item Evans, Steven N.
\item Altshuler, Boris L.
\end{enumerate}
\textbf{List of possible referees}
\begin{enumerate}

\item Nicola Cufaro Petroni, cufaro@ba.infn.it,
Dipartimento di Matematica and TIRES, University of Bari (Ret).
Has done extensive work on the Gompertz model in relation to the Richard's model, connecting it with stochastic growth models and the Logistic (Lotka-Volterra) model. We use their concept of growth rooted in stochastic phenomena.
\item Salvatore De Martino,
demartino247@gmail.com, 
Dipartimento di Ingegneria dell’Informazione ed Elettrica.
Same as above
\item Marcin Molski, mamolski@amu.edu.pl, Adam Mickiewicz University, physics, Gompertz and quantum systems. Has done work on connecting the gompertz model to quantum coherent systems.
\item Francesco Piazza, Francesco.Piazza@cnrs-orleans.fr, Max Planck Institute for the Physics of Complex Systems, physics, SIR models.
Has written one of the central papers modeling covid disease propagation from the SIR perspective. We have based our methods on their paper.
\item Ernesto Estrada, estrada@ifisc.uib-csic.es, Institute of Interdisciplinary Physics and Complex Systems , mathematics, graph theory, SIR models.
Has written a recent paper on the Gompertz model in relation to communicable disease modelling including close connections with graph theoretical concepts used in our paper. 
\item K. Rypdal, kristoffer.rypdal@uit.no, University of Tromsø, mathematics, SIR models.
Has written a paper showing that SIR models become Gompertz in the extreme of the Richard's parameter. We also follow this paper's arguments in our paper.
\item Michael Levitt (NAS Member), michael.levitt@stanford.edu, Stanford University, computational biology, Gompertz models.
Has a preprint on the gompertz model in relation to covid where they leave the explanation of why mortality follows gompertz as an open question.
\item Chris G. Antonopoulos, canton@essex.ac.uk , U. of Essex, physics, chaos and SIR models.
Has written on the SIR model and chaotic dynamics.
\item Gabor Vattay, vattay@elte.hu, Eötvös Loránd University Budapest, physics, SIR models
Has written a paper on SIR models showing that there are ``initial transients'' in the observations which are explained by us in the Gompertz model.
\item E. B. Postnikov, postnikov@kursksu.ru, Kursk State Univesity, physics, SIR models.
Has done work on SIR models using a mean field approach, but has a broach research interest that could be a benefit when reviewing our paper.
\item Both H. Levine and Levin A. in the NAS list would be quite appropriate.
\item L. Kocarev, lkocarev@manu.edu.mk, Macedonian Academy of Sciences and Arts
, physics and mathematics, SIR models.
Has written papers on SIR models as they relate to non-markovian models.

>>>>

\recipient{To}{Editor, \\
               Chaos, Solitons, and Fractals,\\ 
               }
\date{\today}
\opening{\textbf{Initial submission of manuscript titled: ``Unifying Gompertzian growth with the communicable disease spreading paradigm''}}
\closing{Sincerely yours, \vspace{-1em}}

\enclosure[Enclosed ]{
              \\ List of referees
%                  \hspace{0.0em} 5. GATE (2016) \hspace{2em} 9. Identity-Proof (Voter-Id)\\
%                  2. Diploma (MarkSheet/Certificate)
%                  \hspace{1.8em} 6. SLET (2021) \hspace{1.9em} 10. Resume\\        
%                  3. B.Tech (MarkSheet/Certificate)
%                  \hspace{2.3em} 7. UGC-NET (2022) \hspace{-0.1em} \\
%                  4. M.Tech (MarkSheet/Certificate)
%                  \hspace{2.1em} 8. Caste Certificate \\
                 }
\makelettertitle

@@

@@

% \textbf{List of Editorial board members}
% \begin{enumerate}
% \item Levine, Herbert
% \item Levin, Simon A.
% \item Marquet, Pablo A.
% \end{enumerate}

% \textbf{List of NAS members (in order of relevance)} 
% \begin{enumerate}
% \item Levine, Herbert
% \item Levin, Simon A.
% \item Michael Levitt

% \item Nigel D. Goldenfeld 
% \item Evans, Steven N.
% \item Altshuler, Boris L.
% \end{enumerate}
\textbf{List of possible referees}
\begin{enumerate}

\item Nicola Cufaro Petroni, cufaro@ba.infn.it,
Dipartimento di Matematica and TIRES, University of Bari (Ret).
Has done extensive work on the Gompertz model in relation to the Richard's model, connecting it with stochastic growth models and the Logistic (Lotka-Volterra) model. We use their concept of growth rooted in stochastic phenomena.
\item Salvatore De Martino,
demartino247@gmail.com, 
Dipartimento di Ingegneria dell’Informazione ed Elettrica.
Same as above
\item Marcin Molski, mamolski@amu.edu.pl, Adam Mickiewicz University, physics, Gompertz and quantum systems. Has done work on connecting the gompertz model to quantum coherent systems.
\item Francesco Piazza, Francesco.Piazza@cnrs-orleans.fr, Max Planck Institute for the Physics of Complex Systems, physics, SIR models.
Has written one of the central papers modeling covid disease propagation from the SIR perspective. We have based our methods on their paper.
\item Ernesto Estrada, estrada@ifisc.uib-csic.es, Institute of Interdisciplinary Physics and Complex Systems , mathematics, graph theory, SIR models.
Has written a recent paper on the Gompertz model in relation to communicable disease modelling including close connections with graph theoretical concepts used in our paper. 
\item K. Rypdal, kristoffer.rypdal@uit.no, University of Tromsø, mathematics, SIR models.
Has written a paper showing that SIR models become Gompertz in the extreme of the Richard's parameter. We also follow this paper's arguments in our paper.
\item Michael Levitt (NAS Member), michael.levitt@stanford.edu, Stanford University, computational biology, Gompertz models.
Has a preprint on the gompertz model in relation to covid where they leave the explanation of why mortality follows gompertz as an open question.
\item Chris G. Antonopoulos, canton@essex.ac.uk , U. of Essex, physics, chaos and SIR models.
Has written on the SIR model and chaotic dynamics.
\item Gabor Vattay, vattay@elte.hu, Eötvös Loránd University Budapest, physics, SIR models
Has written a paper on SIR models showing that there are ``initial transients'' in the observations which are explained by us in the Gompertz model.
\item E. B. Postnikov, postnikov@kursksu.ru, Kursk State Univesity, physics, SIR models.
Has done work on SIR models using a mean field approach, but has a broach research interest that could be a benefit when reviewing our paper.
\item L. Kocarev, lkocarev@manu.edu.mk, Macedonian Academy of Sciences and Arts
, physics and mathematics, SIR models.
Has written papers on SIR models as they relate to non-markovian models.
